Conflict-Free Vertex Coloring Of Planar Graphs

### 2017-03-21 paper/paper.tex
Adding applications section

@@

% %%%%% REMOVE
% \newpage
% %%%%%

>>>>

\section{Applications}
Before digging into methods for solving the conflict-free coloring problem, it is important to understand why conflict-free coloring is useful. It is useful to know what motivated the recent studies into conflict-free coloring.

\subsection{Wireless Networks}
The main application for conflict-free coloring surrounds wireless networks. Cellular networks, radio, television broadcasting, and satellite communication utilize some form of wireless networks. For each of these systems, a frequency assignment problem arises with specific characteristics.

For example, imagine a cellular network. Cellular networks are heterogeneous networks with two different types of nodes. They have \emph{base-stations} (servers) and \emph{clients}. Base stations are all interconnected through an external backbone network. Clients can only be connected to base stations and connect via radio links. Base stations are each assigned a fixed frequency. Clients, however, are constantly searching frequencies in search for base-stations with good reception.

The problem when initially setting up these networks comes into play when assigning frequencies. Imagine two base-stations near each other having the same frequency. If a client is in reception range of both base-stations, then mutual interference occurs and the radio link is too noisy to be used for proper communication. The goal is to assign frequencies to base stations such that every client is served by some base-station and to minimize the number of frequencies used.

This problem was initially modeled as a vertex coloring problem, where the vertices are the base-stations and the edges are the pairs of base-stations that overlap in their reception range. This model is too wasteful and restrictive. Imagine a situation where a client is within the reception range of 4 base-stations. The VCP model would require 4 colors, one for each base station. If we assign one base-station a color (say red) and the other 3 (say blue), then we only utilize two colors and the client utilizes the red base-station and has no mutual interference. This is exactly what a conflict-free coloring does. \cite{smorodinsky2013conflict}

@@
